### 2019-11-20 analysis/output/include/clust_summ.tex
A day of working with clust4

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Fri, Nov 08, 2019 - 11:40:45
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{clust_summ} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
clust5 & c\_ind & sp\_rich\_raref & n\_stems\_ha & bchave \\ 
\hline \\[-1.8ex] 
C1 & Diplorhynchus condylocarpon, Combretum spp., Pseudolachnostylis maprouneifolia & 7+4.7 & 276+345.2 & 35.3+37.03 \\ 
C2 & Julbernardia paniculata, Isoberlinia angolensis, Albizia antunesiana & 8+4.3 & 274+245.9 & 46.8+35.05 \\ 
C3 & Burkea africana, Pterocarpus angolensis, Baikiaea plurijuga & 4+2.3 & 274+536.5 & 36.3+27.86 \\ 
C4 & Baikiaea plurijuga, Terminalia randii, Albizia amara & 10+5.9 & 447+386.3 & 47+45.41 \\ 
C5 & Colophospermum mopane, Pseudolachnostylis maprouneifolia & 4+2.9 & 322+390.1 & 43.8+34.45 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Nov 20, 2019 - 20:22:20
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{clust_summ} 
\begin{tabular}{@{\extracolsep{5pt}} ccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
clust4 & c\_dom & c\_ind & n\_plots & sp\_rich\_raref & n\_stems\_ha & bchave \\ 
\hline \\[-1.8ex] 
1 & Julbernadia spp., Brachystegia spiciformis, Baikeaea plurijuga & Diplorhynchus condylocarpon, Burkea africana, Pseudolachnostylis maprouneifolia & 734 & 6(5) & 276(208) & 35.4(31.41) \\ 
2 & Julbernadia spp., Brachystegia spp., Isoberlinia angolensis & Julbernardia paniculata, Isoberlinia angolensis, Brachystegia longifolia & 728 & 8(5) & 277(196.9) & 46.9(44.96) \\ 
3 & Spirostachys africana, Senegalia spp., Euclea racemosa & Baikiaea plurijuga, Senegalia ataxacantha, Combretum collinum & 299 & 9(8) & 410(427.7) & 46.6(43.51) \\ 
4 & Colophospermum mopane & Colophospermum mopane, Combretum spp. & 102 & 4(4) & 322(228.8) & 43.8(36.49) \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

### 2019-11-20 analysis/output/include/corr_ci_tab.tex
Finished editing
A day of working with clust4

% Date and time: Thu, Nov 14, 2019 - 15:38:56

@@

Sand \% & Organic C \% & $$-$0.430$ & $$-$0.470$ & $$-$0.390$ & $1387$ & $0$ \\ 
Sand \% & CEC & $$-$0.580$ & $$-$0.610$ & $$-$0.540$ & $1387$ & $0$ \\ 
Sand \% & MAP & $$-$0.420$ & $$-$0.460$ & $$-$0.370$ & $1387$ & $0$ \\ 
Sand \% & MAP CoV & $0.380$ & $0.330$ & $0.420$ & $1387$ & $0$ \\ 
Sand \% & MAT & $0.240$ & $0.190$ & $0.290$ & $1387$ & $0$ \\ 
Sand \% & MAT CoV & $0.140$ & $0.090$ & $0.190$ & $1387$ & $0$ \\ 
Sand \% & Extrap. sp. rich. & $$-$0.290$ & $$-$0.340$ & $$-$0.240$ & $1387$ & $0$ \\ 
Sand \% & Shannon equit. & $$-$0.250$ & $$-$0.300$ & $$-$0.200$ & $1387$ & $0$ \\ 
Sand \% & Tree height CoV & $$-$0.070$ & $$-$0.130$ & $$-$0.010$ & $974$ & $0.024$ \\ 
Sand \% & DBH CoV & $$-$0.180$ & $$-$0.230$ & $$-$0.130$ & $1387$ & $0$ \\ 
Sand \% & Stem density & $$-$0.220$ & $$-$0.260$ & $$-$0.160$ & $1387$ & $0$ \\ 
Sand \% & AGB & $$-$0.190$ & $$-$0.240$ & $$-$0.140$ & $1387$ & $0$ \\ 
Organic C \% & CEC & $0.300$ & $0.250$ & $0.340$ & $1387$ & $0$ \\ 
Organic C \% & MAP & $0.330$ & $0.280$ & $0.380$ & $1387$ & $0$ \\ 
Organic C \% & MAP CoV & $$-$0.350$ & $$-$0.390$ & $$-$0.300$ & $1387$ & $0$ \\ 
Organic C \% & MAT & $$-$0.310$ & $$-$0.350$ & $$-$0.260$ & $1387$ & $0$ \\ 
Organic C \% & MAT CoV & $0$ & $$-$0.050$ & $0.050$ & $1387$ & $0.996$ \\ 
Organic C \% & Extrap. sp. rich. & $0.150$ & $0.100$ & $0.200$ & $1387$ & $0$ \\ 
Organic C \% & Shannon equit. & $0.140$ & $0.090$ & $0.190$ & $1387$ & $0$ \\ 
Organic C \% & Tree height CoV & $0.010$ & $$-$0.050$ & $0.080$ & $974$ & $0.663$ \\ 
Organic C \% & DBH CoV & $0.100$ & $0.050$ & $0.160$ & $1387$ & $0$ \\ 
Organic C \% & Stem density & $0.070$ & $0.010$ & $0.120$ & $1387$ & $0.015$ \\ 
Organic C \% & AGB & $0.200$ & $0.150$ & $0.250$ & $1387$ & $0$ \\ 
CEC & MAP & $$-$0.060$ & $$-$0.120$ & $$-$0.010$ & $1387$ & $0.016$ \\ 
CEC & MAP CoV & $$-$0.560$ & $$-$0.590$ & $$-$0.520$ & $1387$ & $0$ \\ 
CEC & MAT & $0.240$ & $0.190$ & $0.290$ & $1387$ & $0$ \\ 
CEC & MAT CoV & $0.080$ & $0.030$ & $0.130$ & $1387$ & $0.002$ \\ 
CEC & Extrap. sp. rich. & $$-$0.070$ & $$-$0.120$ & $$-$0.020$ & $1387$ & $0.011$ \\ 
CEC & Shannon equit. & $0.240$ & $0.190$ & $0.280$ & $1387$ & $0$ \\ 
CEC & Tree height CoV & $0.060$ & $0$ & $0.130$ & $974$ & $0.044$ \\ 
CEC & DBH CoV & $0.250$ & $0.200$ & $0.300$ & $1387$ & $0$ \\ 
CEC & Stem density & $0.210$ & $0.160$ & $0.260$ & $1387$ & $0$ \\ 
CEC & AGB & $0.050$ & $0$ & $0.100$ & $1387$ & $0.053$ \\ 
MAP & MAP CoV & $$-$0.080$ & $$-$0.140$ & $$-$0.030$ & $1387$ & $0.002$ \\ 
MAP & MAT & $$-$0.080$ & $$-$0.130$ & $$-$0.030$ & $1387$ & $0.003$ \\ 
MAP & MAT CoV & $$-$0.650$ & $$-$0.680$ & $$-$0.620$ & $1387$ & $0$ \\ 
MAP & Extrap. sp. rich. & $0.310$ & $0.270$ & $0.360$ & $1387$ & $0$ \\ 
MAP & Shannon equit. & $$-$0.020$ & $$-$0.080$ & $0.030$ & $1387$ & $0.382$ \\ 
MAP & Tree height CoV & $0.180$ & $0.120$ & $0.240$ & $974$ & $0$ \\ 
MAP & DBH CoV & $0.060$ & $0.010$ & $0.110$ & $1387$ & $0.025$ \\ 
MAP & Stem density & $$-$0.070$ & $$-$0.120$ & $$-$0.010$ & $1387$ & $0.013$ \\ 
MAP & AGB & $0.140$ & $0.090$ & $0.190$ & $1387$ & $0$ \\ 
MAP CoV & MAT & $$-$0.170$ & $$-$0.220$ & $$-$0.110$ & $1387$ & $0$ \\ 
MAP CoV & MAT CoV & $0.020$ & $$-$0.040$ & $0.070$ & $1387$ & $0.561$ \\ 
MAP CoV & Extrap. sp. rich. & $0.080$ & $0.020$ & $0.130$ & $1387$ & $0.005$ \\ 
MAP CoV & Shannon equit. & $$-$0.230$ & $$-$0.280$ & $$-$0.180$ & $1387$ & $0$ \\ 
MAP CoV & Tree height CoV & $$-$0.050$ & $$-$0.110$ & $0.010$ & $974$ & $0.102$ \\ 
MAP CoV & DBH CoV & $$-$0.350$ & $$-$0.390$ & $$-$0.300$ & $1387$ & $0$ \\ 
MAP CoV & Stem density & $$-$0.250$ & $$-$0.300$ & $$-$0.200$ & $1387$ & $0$ \\ 
MAP CoV & AGB & $$-$0.100$ & $$-$0.160$ & $$-$0.050$ & $1387$ & $0$ \\ 
MAT & MAT CoV & $$-$0.330$ & $$-$0.370$ & $$-$0.280$ & $1387$ & $0$ \\ 
MAT & Extrap. sp. rich. & $$-$0.230$ & $$-$0.280$ & $$-$0.180$ & $1387$ & $0$ \\ 
MAT & Shannon equit. & $0.010$ & $$-$0.040$ & $0.060$ & $1387$ & $0.775$ \\ 
MAT & Tree height CoV & $0.100$ & $0.040$ & $0.160$ & $974$ & $0.002$ \\ 
MAT & DBH CoV & $0.090$ & $0.040$ & $0.150$ & $1387$ & $0$ \\ 
MAT & Stem density & $0.080$ & $0.030$ & $0.130$ & $1387$ & $0.003$ \\ 
MAT & AGB & $$-$0.060$ & $$-$0.110$ & $0$ & $1387$ & $0.038$ \\ 
MAT CoV & Extrap. sp. rich. & $$-$0.240$ & $$-$0.290$ & $$-$0.190$ & $1387$ & $0$ \\ 
MAT CoV & Shannon equit. & $$-$0.030$ & $$-$0.090$ & $0.020$ & $1387$ & $0.193$ \\ 
MAT CoV & Tree height CoV & $$-$0.120$ & $$-$0.180$ & $$-$0.060$ & $974$ & $0$ \\ 
MAT CoV & DBH CoV & $$-$0.020$ & $$-$0.070$ & $0.030$ & $1387$ & $0.428$ \\ 
MAT CoV & Stem density & $$-$0.070$ & $$-$0.120$ & $$-$0.020$ & $1387$ & $0.010$ \\ 
MAT CoV & AGB & $$-$0.080$ & $$-$0.140$ & $$-$0.030$ & $1387$ & $0.002$ \\ 
Extrap. sp. rich. & Shannon equit. & $0.540$ & $0.500$ & $0.580$ & $1387$ & $0$ \\ 
Extrap. sp. rich. & Tree height CoV & $0.070$ & $0$ & $0.130$ & $974$ & $0.038$ \\ 
Extrap. sp. rich. & DBH CoV & $0.160$ & $0.110$ & $0.210$ & $1387$ & $0$ \\ 
Extrap. sp. rich. & Stem density & $0.390$ & $0.350$ & $0.440$ & $1387$ & $0$ \\ 
Extrap. sp. rich. & AGB & $0.460$ & $0.420$ & $0.500$ & $1387$ & $0$ \\ 
Shannon equit. & Tree height CoV & $$-$0.060$ & $$-$0.130$ & $0$ & $974$ & $0.046$ \\ 
Shannon equit. & DBH CoV & $0.140$ & $0.090$ & $0.190$ & $1387$ & $0$ \\ 
Shannon equit. & Stem density & $0.540$ & $0.500$ & $0.580$ & $1387$ & $0$ \\ 
Shannon equit. & AGB & $0.400$ & $0.350$ & $0.440$ & $1387$ & $0$ \\ 
Tree height CoV & DBH CoV & $0.530$ & $0.480$ & $0.570$ & $974$ & $0$ \\ 
Tree height CoV & Stem density & $$-$0.030$ & $$-$0.100$ & $0.030$ & $974$ & $0.311$ \\ 
Tree height CoV & AGB & $0.210$ & $0.150$ & $0.270$ & $974$ & $0$ \\ 
DBH CoV & Stem density & $0.190$ & $0.140$ & $0.240$ & $1387$ & $0$ \\ 
DBH CoV & AGB & $0.420$ & $0.380$ & $0.470$ & $1387$ & $0$ \\ 
Stem density & AGB & $0.510$ & $0.470$ & $0.540$ & $1387$ & $0$ \\ 

>>>>

% Date and time: Wed, Nov 20, 2019 - 15:22:31

@@

sand\_per\_std & ocdens\_std & $$-$0.500$ & $$-$0.540$ & $$-$0.470$ & $1766$ & $0$ \\ 
sand\_per\_std & cation\_ex\_cap\_std & $$-$0.560$ & $$-$0.600$ & $$-$0.530$ & $1766$ & $0$ \\ 
sand\_per\_std & total\_precip\_std & $$-$0.490$ & $$-$0.520$ & $$-$0.450$ & $1766$ & $0$ \\ 
sand\_per\_std & precip\_seasonality\_log\_std & $0.330$ & $0.280$ & $0.370$ & $1766$ & $0$ \\ 
sand\_per\_std & mean\_temp\_std & $0.290$ & $0.250$ & $0.330$ & $1766$ & $0$ \\ 
sand\_per\_std & temp\_seasonality\_log\_std & $0.220$ & $0.180$ & $0.270$ & $1766$ & $0$ \\ 
sand\_per\_std & sp\_rich\_raref\_log\_std & $$-$0.360$ & $$-$0.400$ & $$-$0.310$ & $1766$ & $0$ \\ 
sand\_per\_std & shannon\_equit\_log\_std & $$-$0.300$ & $$-$0.340$ & $$-$0.260$ & $1766$ & $0$ \\ 
sand\_per\_std & cov\_height\_std & $$-$0.120$ & $$-$0.170$ & $$-$0.060$ & $1326$ & $0$ \\ 
sand\_per\_std & cov\_dbh\_std & $$-$0.190$ & $$-$0.230$ & $$-$0.140$ & $1766$ & $0$ \\ 
sand\_per\_std & stems\_ha\_log\_std & $$-$0.270$ & $$-$0.310$ & $$-$0.230$ & $1766$ & $0$ \\ 
sand\_per\_std & bchave\_log & $$-$0.230$ & $$-$0.280$ & $$-$0.190$ & $1766$ & $0$ \\ 
ocdens\_std & cation\_ex\_cap\_std & $0.300$ & $0.250$ & $0.340$ & $1766$ & $0$ \\ 
ocdens\_std & total\_precip\_std & $0.440$ & $0.400$ & $0.480$ & $1766$ & $0$ \\ 
ocdens\_std & precip\_seasonality\_log\_std & $$-$0.310$ & $$-$0.350$ & $$-$0.270$ & $1766$ & $0$ \\ 
ocdens\_std & mean\_temp\_std & $$-$0.310$ & $$-$0.350$ & $$-$0.270$ & $1766$ & $0$ \\ 
ocdens\_std & temp\_seasonality\_log\_std & $$-$0.140$ & $$-$0.190$ & $$-$0.100$ & $1766$ & $0$ \\ 
ocdens\_std & sp\_rich\_raref\_log\_std & $0.260$ & $0.210$ & $0.300$ & $1766$ & $0$ \\ 
ocdens\_std & shannon\_equit\_log\_std & $0.220$ & $0.180$ & $0.270$ & $1766$ & $0$ \\ 
ocdens\_std & cov\_height\_std & $0.070$ & $0.020$ & $0.130$ & $1326$ & $0.006$ \\ 
ocdens\_std & cov\_dbh\_std & $0.140$ & $0.090$ & $0.190$ & $1766$ & $0$ \\ 
ocdens\_std & stems\_ha\_log\_std & $0.170$ & $0.120$ & $0.210$ & $1766$ & $0$ \\ 
ocdens\_std & bchave\_log & $0.250$ & $0.200$ & $0.290$ & $1766$ & $0$ \\ 
cation\_ex\_cap\_std & total\_precip\_std & $$-$0.010$ & $$-$0.060$ & $0.040$ & $1766$ & $0.657$ \\ 
cation\_ex\_cap\_std & precip\_seasonality\_log\_std & $$-$0.510$ & $$-$0.540$ & $$-$0.480$ & $1766$ & $0$ \\ 
cation\_ex\_cap\_std & mean\_temp\_std & $0.190$ & $0.150$ & $0.240$ & $1766$ & $0$ \\ 
cation\_ex\_cap\_std & temp\_seasonality\_log\_std & $0.030$ & $$-$0.020$ & $0.070$ & $1766$ & $0.260$ \\ 
cation\_ex\_cap\_std & sp\_rich\_raref\_log\_std & $$-$0.020$ & $$-$0.060$ & $0.030$ & $1766$ & $0.464$ \\ 
cation\_ex\_cap\_std & shannon\_equit\_log\_std & $0.220$ & $0.170$ & $0.260$ & $1766$ & $0$ \\ 
cation\_ex\_cap\_std & cov\_height\_std & $0.040$ & $$-$0.010$ & $0.090$ & $1326$ & $0.149$ \\ 
cation\_ex\_cap\_std & cov\_dbh\_std & $0.240$ & $0.190$ & $0.280$ & $1766$ & $0$ \\ 
cation\_ex\_cap\_std & stems\_ha\_log\_std & $0.200$ & $0.150$ & $0.240$ & $1766$ & $0$ \\ 
cation\_ex\_cap\_std & bchave\_log & $0.030$ & $$-$0.020$ & $0.080$ & $1766$ & $0.230$ \\ 
total\_precip\_std & precip\_seasonality\_log\_std & $$-$0.120$ & $$-$0.160$ & $$-$0.070$ & $1766$ & $0$ \\ 
total\_precip\_std & mean\_temp\_std & $$-$0.120$ & $$-$0.170$ & $$-$0.070$ & $1766$ & $0$ \\ 
total\_precip\_std & temp\_seasonality\_log\_std & $$-$0.690$ & $$-$0.720$ & $$-$0.670$ & $1766$ & $0$ \\ 
total\_precip\_std & sp\_rich\_raref\_log\_std & $0.430$ & $0.390$ & $0.470$ & $1766$ & $0$ \\ 
total\_precip\_std & shannon\_equit\_log\_std & $0.100$ & $0.060$ & $0.150$ & $1766$ & $0$ \\ 
total\_precip\_std & cov\_height\_std & $0.250$ & $0.200$ & $0.300$ & $1326$ & $0$ \\ 
total\_precip\_std & cov\_dbh\_std & $0.150$ & $0.100$ & $0.190$ & $1766$ & $0$ \\ 
total\_precip\_std & stems\_ha\_log\_std & $0.070$ & $0.030$ & $0.120$ & $1766$ & $0.002$ \\ 
total\_precip\_std & bchave\_log & $0.210$ & $0.170$ & $0.260$ & $1766$ & $0$ \\ 
precip\_seasonality\_log\_std & mean\_temp\_std & $$-$0.170$ & $$-$0.210$ & $$-$0.120$ & $1766$ & $0$ \\ 
precip\_seasonality\_log\_std & temp\_seasonality\_log\_std & $0.070$ & $0.020$ & $0.120$ & $1766$ & $0.003$ \\ 
precip\_seasonality\_log\_std & sp\_rich\_raref\_log\_std & $$-$0.010$ & $$-$0.060$ & $0.040$ & $1766$ & $0.708$ \\ 
precip\_seasonality\_log\_std & shannon\_equit\_log\_std & $$-$0.240$ & $$-$0.280$ & $$-$0.200$ & $1766$ & $0$ \\ 
precip\_seasonality\_log\_std & cov\_height\_std & $$-$0.010$ & $$-$0.060$ & $0.050$ & $1326$ & $0.768$ \\ 
precip\_seasonality\_log\_std & cov\_dbh\_std & $$-$0.340$ & $$-$0.380$ & $$-$0.300$ & $1766$ & $0$ \\ 
precip\_seasonality\_log\_std & stems\_ha\_log\_std & $$-$0.260$ & $$-$0.300$ & $$-$0.210$ & $1766$ & $0$ \\ 
precip\_seasonality\_log\_std & bchave\_log & $$-$0.100$ & $$-$0.140$ & $$-$0.050$ & $1766$ & $0$ \\ 
mean\_temp\_std & temp\_seasonality\_log\_std & $$-$0.310$ & $$-$0.350$ & $$-$0.270$ & $1766$ & $0$ \\ 
mean\_temp\_std & sp\_rich\_raref\_log\_std & $$-$0.180$ & $$-$0.220$ & $$-$0.130$ & $1766$ & $0$ \\ 
mean\_temp\_std & shannon\_equit\_log\_std & $0$ & $$-$0.050$ & $0.040$ & $1766$ & $0.901$ \\ 
mean\_temp\_std & cov\_height\_std & $0.100$ & $0.050$ & $0.160$ & $1326$ & $0$ \\ 
mean\_temp\_std & cov\_dbh\_std & $0.140$ & $0.100$ & $0.190$ & $1766$ & $0$ \\ 
mean\_temp\_std & stems\_ha\_log\_std & $0.050$ & $0.010$ & $0.100$ & $1766$ & $0.024$ \\ 
mean\_temp\_std & bchave\_log & $$-$0.080$ & $$-$0.130$ & $$-$0.030$ & $1766$ & $0.001$ \\ 
temp\_seasonality\_log\_std & sp\_rich\_raref\_log\_std & $$-$0.340$ & $$-$0.380$ & $$-$0.300$ & $1766$ & $0$ \\ 
temp\_seasonality\_log\_std & shannon\_equit\_log\_std & $$-$0.130$ & $$-$0.180$ & $$-$0.090$ & $1766$ & $0$ \\ 
temp\_seasonality\_log\_std & cov\_height\_std & $$-$0.220$ & $$-$0.280$ & $$-$0.170$ & $1326$ & $0$ \\ 
temp\_seasonality\_log\_std & cov\_dbh\_std & $$-$0.140$ & $$-$0.190$ & $$-$0.100$ & $1766$ & $0$ \\ 
temp\_seasonality\_log\_std & stems\_ha\_log\_std & $$-$0.150$ & $$-$0.200$ & $$-$0.110$ & $1766$ & $0$ \\ 
temp\_seasonality\_log\_std & bchave\_log & $$-$0.140$ & $$-$0.190$ & $$-$0.100$ & $1766$ & $0$ \\ 
sp\_rich\_raref\_log\_std & shannon\_equit\_log\_std & $0.600$ & $0.570$ & $0.630$ & $1766$ & $0$ \\ 
sp\_rich\_raref\_log\_std & cov\_height\_std & $0.280$ & $0.230$ & $0.330$ & $1326$ & $0$ \\ 
sp\_rich\_raref\_log\_std & cov\_dbh\_std & $0.320$ & $0.270$ & $0.360$ & $1766$ & $0$ \\ 
sp\_rich\_raref\_log\_std & stems\_ha\_log\_std & $0.510$ & $0.480$ & $0.540$ & $1766$ & $0$ \\ 
sp\_rich\_raref\_log\_std & bchave\_log & $0.490$ & $0.460$ & $0.530$ & $1766$ & $0$ \\ 
shannon\_equit\_log\_std & cov\_height\_std & $0.100$ & $0.040$ & $0.150$ & $1326$ & $0$ \\ 
shannon\_equit\_log\_std & cov\_dbh\_std & $0.250$ & $0.200$ & $0.290$ & $1766$ & $0$ \\ 
shannon\_equit\_log\_std & stems\_ha\_log\_std & $0.610$ & $0.580$ & $0.640$ & $1766$ & $0$ \\ 
shannon\_equit\_log\_std & bchave\_log & $0.430$ & $0.390$ & $0.470$ & $1766$ & $0$ \\ 
cov\_height\_std & cov\_dbh\_std & $0.580$ & $0.550$ & $0.620$ & $1326$ & $0$ \\ 
cov\_height\_std & stems\_ha\_log\_std & $0.170$ & $0.110$ & $0.220$ & $1326$ & $0$ \\ 
cov\_height\_std & bchave\_log & $0.290$ & $0.240$ & $0.340$ & $1326$ & $0$ \\ 
cov\_dbh\_std & stems\_ha\_log\_std & $0.330$ & $0.280$ & $0.370$ & $1766$ & $0$ \\ 
cov\_dbh\_std & bchave\_log & $0.450$ & $0.410$ & $0.480$ & $1766$ & $0$ \\ 
stems\_ha\_log\_std & bchave\_log & $0.560$ & $0.530$ & $0.590$ & $1766$ & $0$ \\ 
